A statistical assessment of influenza intensity thresholds from the moving epidemic and WHO methods

### 2023-07-13 Draft/Draft_MEM.tex
Minor changes.

To make notation more intuitive we also write $\sigma^2_i = \sigma_{i, i}$. Construction of thresholds is based on the reference set $\mathcal{Y}$, which pools the elements of the vectors $\mathbf{Y}_1, \dots, \mathbf{Y}_m$. It can be shown that the expectations of $\bar{Y}$ and $S^2$ as defined in equation \eqref{eq:moments} are given by

@@

@@

We would like to thank Michael H\"ohle, Rob Moss, Laura Werlen and Daniel Wolffram for helpful discussions. Johannes Bracher was supported by the Helmholtz Foundation via the SIMCARD Information and Data Science Pilot Project as well as Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) -- project number 512483310.

>>>>

To make notation more intuitive we also write $\sigma^2_i = \sigma_{i, i}$. Construction of thresholds is based on the reference set $\mathcal{Y}$, which pools the elements of the vectors $\mathbf{Y}_1, \dots, \mathbf{Y}_m$. It can be shown that the expectations of the empirical mean $\bar{Y}$ and variance $S^2$ of the observations in the reference set (see in equation) \eqref{eq:moments} are given by

@@

In our two empirical examples we found the normal distribution to provide a quite good fit to the distribution of log-transformed season peak incidences. However, it is unclear how generalizable this is. For indicators which represent fractions, like positivity percentages, it may not be a suitable choice as in principle the threshold for high or very high activity could be above 100\%. Then different transformations (like the logit) or distributional assumptions would be necessary. For the US ILI percentages, no practical problem arose, but this may well be the case for other indicators.

@@

We would like to thank Sebastian Funk, Michael H\"ohle, Rob Moss, Laura Werlen and Daniel Wolffram for helpful discussions. Johannes Bracher was supported by the Helmholtz Foundation via the SIMCARD Information and Data Science Pilot Project as well as Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) -- project number 512483310.
